Title Goes Here

### 2019-03-31 analysis/paper/paper.Rmd
Update paper.Rmd

```{r tidy-data, eval = FALSE}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))

@@

```{r-gganimate}
# test gganimate for measurement of beads by period
devtools::install_github('thomasp85/gganimate')
library(gganimate)

>>>>

```{r tidy-data2, eval = FALSE}
# 40 sampling units
sample_units <-
  AD_data %>% 
  semi_join(units_40, by = c (`坑號` = "the_sq"))

@@

```{r-gganimate}
# test gganimate for measurement of beads by period
# devtools::install_github('thomasp85/gganimate')
library(gganimate)
